Accelerating adaptive ultrasound algorithms using graphics processing units \vspace{0.5cm}

### 2014-01-04 ThesisJP/Introduction/introduction.tex
Finished layout.

\section{Background and motivation}

@@

\section{Summary of presented work}

\subsubsection{Paper I:\\
An Optimised GPU Implementation of the MVDR Beamformer for Active Sonar Imaging}

{\it Submitted for review to IEEE Transactions on Oceanic Engineering.}
\vspace{0.3 cm}

Summary of paper...

\vspace{0.3 cm}
\emph{The work was a joint effort with PhD student ...}

\subsubsection{Paper II:\\
Implementing Capon Beamforming on a GPU for Real-Time Cardiac Ultrasound Imaging}

{\it IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control, vol. XY, January 2014.}
\vspace{0.3 cm}

Summary of paper...

\vspace{0.3 cm}
\emph{The work was a joint effort with PhD student ...}

\subsubsection{Paper no. 3 (Chapter 5):\\
Capon Beamforming Applied on Moving Objects - An Analysis of Local Lateral Shift-Invariance}

{\it Submitted for review to IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control.}
\vspace{0.3 cm}

Summary of paper...

\subsubsection{Paper no. 4 (Chapter 6):\\
Adaptive Volume Rendering of Cardiac 3D Ultrasound Images - Utilizing Blood Pool Statistics}

{\it Proc. SPIE Medical Imaging 2012}
\vspace{0.3 cm}

Summary of paper...

\subsubsection{Paper no. 5 (Chapter 7):\\
Huygens on Speed: Interactive Simulation of Ultrasound Pressure Fields}

{\it Proc. IEEE Ultrasonics Symposium 2012}
\vspace{0.3 cm}

Summary of paper...

>>>>

\section{Motivation}

@@

\section{Summary of papers}

\subsection{Paper I}
\textbf{An Optimised GPU Implementation of the MVDR Beamformer for Active Sonar Imaging}\\
J. I. Buskenes, \textbf{J. P. \AA{}sen}, C.-I. C. Nilsen and A. Austeng\\
{\it IEEE Transactions on Oceanic Engineering, submitted.}\\\\
Summary of paper...

\subsection{Paper II}
\textbf{Implementing Capon Beamforming on a GPU for Real-Time Cardiac Ultrasound Imaging}\\
\textbf{J. P. \AA{}sen}, J. I. Buskenes, C.-I. C. Nilsen, A. Austeng and S. Holm\\
{\it IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control, vol. 61, no. 1, pp. \todo{add pages}, Jan. 2014.}\\\\
Summary of paper...

\subsection{Paper III}
\textbf{Capon Beamforming and Moving Objects - An Analysis of Lateral Shift-Invariance}\\
\textbf{J. P. \AA{}sen}, A. Austeng and S. Holm\\
{\it IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control, submitted.}
Summary of paper...

\subsection{Paper IV}
\textbf{Adaptive Volume Rendering of Cardiac 3D Ultrasound Images - Utilizing Blood Pool Statistics}\\
\textbf{J. P. \AA{}sen}, E. Steen, G. Kiss, A. Thorstensen and S. I. Rabben\\
{\it Proc. SPIE Medical Imaging 2012, \todo{add pages}.}\\\\
Summary of paper...

\subsection{Paper V}
\textbf{Huygens on Speed: Interactive Simulation of Ultrasound Pressure Fields}\\
\textbf{J. P. \AA{}sen} and S. Holm
{\it Proc. IEEE Ultrasonics Symposium 2012 \todo{add pages}.}\\\\
Summary of paper...

### 2014-01-04 ThesisJP/Thesis.tex
Finished layout.

%Norw.  sammendrag
% Norsk sammendrag
%\Chapter*{}
\newpage%
~\\
\vspace{10.0cm}
~\\
{\bf NTNU}
\\
Norwegian University of Science and Technology\\
\\
Thesis for the degree of Philosophiae Doctor\\
\\
Faculty of Medicine\\
Department of Circulation and Medical Imaging\\
\\
\copyright\,Jon Petter \AA{}sen\\
\\
ISBN XXX-XX-XXX-XXXX-X (printed version)\\
ISBN XXX-XX-XXX-XXXX-X (electronic version)\\
ISSN XX-XX\\
\\
Doctoral theses at NTNU, 20014:XX\\
\\
Printed by NTNU-trykk

~\\
\newpage
\thispagestyle{empty}%
~\\%
~\\%
~\\
\noindent\large 
Sammendrag p\aa{} norsk.
%\vspace{0.2cm}\\%
\\\\%
\normalsize
\todo{Skriv sammendrag p\aa{} norsk}

@@

% ENGLISH ABSTRACT / SUMMARY
\CustChapter*{Abstract}
%\chapter*{Abstract}
\thispagestyle{empty}%
\todo{Write abstract ...}

@@

% PREFACE AND ACKNOWLEDGEMENTS
\CustChapter*{Preface}%
\thispagestyle{empty}%
The present thesis is submitted in partial fulfillment of the requirements for the degree of \textit{Philosophiae Doctor} (Ph.D.) at the Faculty of Medicine at the Norwegian University of Science and Technology (NTNU). The research was funded by \textit{Medical Imaging Laboratory} (MI-Lab), and was carried out at the Department of Circulation and Medical Imaging. The main supervisor has been Professor Sverre Holm  in the Department of Informatics, University of Oslo, and Professor II at MI-Lab. Co-supervisors have been PhD Stein Inge Rabben, PhD Erik Steen and Professor Hans Torp.

@@

\CustChapter*{List of publications}
This thesis is based on the following five papers, referred to in the text by their Roman numerals (I-V): 
\begin{enumerate}[I]
\renewcommand\labelenumi{\bfseries\theenumi}
	\item J. I. Buskenes, \textbf{J. P. \AA{}sen}, C.-I. C. Nilsen and A. Austeng, "An optimised GPU implementation of the MVDR beamformer for active sonar imaging", {\it  IEEE Transactions on Oceanic Engineering, submitted}.
	\item \textbf{J. P. \AA{}sen}, J. I. Buskenes, C.-I. C. Nilsen, A. Austeng and S. Holm, "Implementing Capon beamforming on a GPU for real-time cardiac ultrasound imaging", {\it IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control, vol. 61, no. 1, pp. \todo{add pages} January 2014}.
 	\item \textbf{J. P. \AA{}sen}, A. Austeng and S. Holm, "Capon beamforming and moving objects - An analysis of lateral shift-invariance", {\it IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control, submitted}.
	\item \textbf{J. P. \AA{}sen}, E. Steen, G. Kiss, A. Thorstensen and S. I. Rabben, "Adaptive volume rendering of cardiac 3D ultrasound images - utilizing blood pool statistics", {\it Proc. SPIE Medical Imaging 2012 \todo{add pages}}.
	\item \textbf{J. P. \AA{}sen} and S. Holm, "Huygens on speed: Interactive simulation of ultrasound pressure fields", {\it Proc. IEEE Ultrasonics Symposium 2012 \todo{add pages}}.
\end{enumerate}

\CustChapter*{Related publications}
The following papers are related to the included papers, and are referred to in the text by their Roman numerals:

@@

	\item \textbf{J. P. \AA{}sen}, J. I. Buskenes, C.-I. C. Nilsen, A. Austeng and S. Holm, "Implementing Capon Beamforming on the GPU for Real-Time Cardiac Ultrasound Imaging", {\it Proc. IEEE Ultrasonics Symposium 2012}.

	\item J. I. Buskenes, \textbf{J. P. \AA{}sen}, C.-I. C. Nilsen and A. Austeng, "Adapting the Minimum variance beamformer to a graphics processing unit for active sonar imaging systems", {\it Proc. Meetings on Acoustics 2013}.

	\item G. Kiss, E. Steen, \textbf{J. P \AA{}sen} and H. Torp, "GPU volume rendering in 3D echocardiography: real-time pre-processing and ray-casting", {\it Proc. IEEE Ultrasonics Symposium 2010}.

@@

	\item E. S. Br\o{}nstad, \textbf{J. P. \AA{}sen}, H. Torp and G. Kiss, "Visibility driven visualization of 3D cardiac ultrasound data on the GPU", {\it Proc. IEEE Ultrasonics Symposium 2012}.
\end{enumerate}

\newpage\thispagestyle{empty}
\pagestyle{fancy}
%
\tableofcontents

%%%% CHAPTER 1 %%%%
\begin{bibunit}[ieeetr]
\CustChapter{Introduction} 
\runningtitle{Introduction}
\input{./Introduction/introduction}
\newpage\addcontentsline{toc}{section}{References}
\putbib[bibIntroduction]
\end{bibunit}

%%%% CHAPTER 2 %%%%
\begin{bibunit}[ieeetr]
\CustChapter{Background} 
\runningtitle{Background}
\input{./Background/background}
\newpage\addcontentsline{toc}{section}{References}
\putbib[bibBackground]
\end{bibunit}

%%%% Paper 1 %%%%
\begin{bibunit}[ieeetr]
\CustChapter{An Optimised GPU Implementation of the MVDR Beamformer for Active Sonar Imaging}
\runningtitle{An Optimised GPU Implementation of the MVDR Beamformer for Active Sonar Imaging}
\authors{
	Jo Inge Buskenes$^{1}$, 
    	Jon Petter \AA{}sen$^{2}$, 
    	Carl-Inge C. Nilsen$^{1}$ and
    	Andreas Austeng$^{1}$
} 
{
	$^{1}$Department of Informatics, University of Oslo, Oslo, Norway\\
    	$^{2}$Medical Imaging Lab (MI-Lab), Norwegian University of Science and Technology, Trondheim, Norway
}
\noindent \textit{Submitted for review to IEEE Transactions on Oceanic Engineering}
%\input{./STB/STB_manuscript}
\newpage\addcontentsline{toc}{section}{References}
\putbib[bibSTB]
\end{bibunit}

%%%% Paper 2 %%%%
\begin{bibunit}[ieeetr]
\CustChapter{Implementing Capon Beamforming on a GPU for Real-Time Cardiac Ultrasound Imaging}
\runningtitle{Implementing Capon Beamforming on a GPU for Real-Time Cardiac Ultrasound Imaging}
\authors{
	Jon Petter \AA{}sen$^{1}$,
    	Jo Inge Buskenes$^{2}$,  
    	Carl-Inge C. Nilsen$^{2}$,
    	Andreas Austeng$^{2}$ and
    	Sverre Holm$^{1,2}$
} 
{
	$^{1}$Medical Imaging Lab (MI-Lab), Norwegian University of Science and Technology, Trondheim, Norway\\
    	$^{2}$Department of Informatics, University of Oslo, Oslo, Norway
}
\noindent \textit{IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control, vol. XY, January 2014}
%\input{./MLAandAb/Aberration_HiFR}
\newpage\addcontentsline{toc}{section}{References}
\putbib[bibMLAandAb]
\end{bibunit}

%%%% Paper 3 %%%%
\begin{bibunit}[ieeetr]
\CustChapter{Capon Beamforming Applied on Moving Objects - An Analysis of Local Lateral Shift-Invariance}
\runningtitle{Capon Beamforming Applied on Moving Objects - An Analysis of Local Lateral Shift-Invariance}
\authors{
	Jon Petter \AA{}sen$^{1}$, 
    	Andreas Austeng$^{2}$ and
    	Sverre Holm$^{1,2}$
} 
{
	$^{1}$Medical Imaging Lab (MI-Lab), Norwegian University of Science and Technology, Trondheim, Norway\\
    	$^{2}$Department of Informatics, University of Oslo, Oslo, Norway
}
\noindent \textit{Submitted for review to IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control}
%\input{./STBandAb/STBandAberration}
\newpage\addcontentsline{toc}{section}{References}
\putbib[bibSTBandAb]
\end{bibunit}

%%%% Paper 4 %%%%
\begin{bibunit}[ieeetr]
\CustChapter{Adaptive Volume Rendering of Cardiac 3D Ultrasound Images - Utilizing Blood Pool Statistics}
\runningtitle{Adaptive Volume Rendering of Cardiac 3D Ultrasound Images - Utilizing Blood Pool Statistics}
\authors{
	Jon Petter \AA{}sen$^{1}$,
	Erik Steen$^2$,
	Gabriel Kiss$^{3,4}$,
	Anders Thorstensen$^{1,5}$,
	Stein Inge Rabben$^2$
}
{
$^{1}$Medical Imaging Lab (MI-Lab), Norwegian University of Science and Technology, Trondheim, Norway\\
$^{2}$ GE Vingmed Ultrasound, Horten, Norway\\
$^{3}$ Norwegian University of Science and Technology, ISB - Department of Circulation and Medical Imaging, Trondheim, Norway\\
$^{4}$ St. Olavs Hospital, Trondheim, Norway\\
$^{5}$ Department of Cardiology, St. Olavs Hospital, Trondheim, Norway
}
\noindent \textit{Proc. SPIE Medical Imaging 2012}
%\input{./SPTD/StbSinglePulseTissueDoppler}
\newpage\addcontentsline{toc}{section}{References}
\putbib[bibSPTD]
\end{bibunit}

%%%% Paper 5 %%%%
\begin{bibunit}[ieeetr]
\CustChapter{Huygens on Speed: Interactive Simulation of Ultrasound Pressure Fields}
\runningtitle{Huygens on speed: Interactive simulation of ultrasound pressure fields}
\authors{Jon Petter \AA{}sen$^1$ and Sverre Holm$^{1,2}$}
{
	$^{1}$Medical Imaging Lab (MI-Lab), Norwegian University of Science and Technology, Trondheim, Norway\\
    	$^{2}$Department of Informatics, University of Oslo, Oslo, Norway
}
\noindent \textit{Proc. IEEE Ultrasonics Symposium 2012}
%\input{./SPTD/StbSinglePulseTissueDoppler}
\newpage\addcontentsline{toc}{section}{References}
\putbib[bibSPTD]
\end{bibunit}

>>>>

%Norw.  sammendrag
% Norsk sammendrag
%\Chapter*{}
\newpage%

\renewcommand{\thepage}{\roman{page}}% Roman numerals for page counter

~\\
\vspace{10.0cm}
~\\
{\bf NTNU}
\\
Norwegian University of Science and Technology\\
\\
Thesis for the degree of Philosophiae Doctor\\
\\
Faculty of Medicine\\
Department of Circulation and Medical Imaging\\
\\
\copyright\,Jon Petter \AA{}sen\\
\\
ISBN XXX-XX-XXX-XXXX-X (printed version)\\
ISBN XXX-XX-XXX-XXXX-X (electronic version)\\
ISSN XX-XX\\
\\
Doctoral theses at NTNU, 20014:XX\\
\\
Printed by NTNU-trykk

~\\
\newpage
%\thispagestyle{empty}%
~\\%
~\\%
~\\
\noindent\large 
Sammendrag p\aa{} norsk.
%\vspace{0.2cm}\\%
\\\\%
\normalsize
\todo{Skriv sammendrag p\aa{} norsk}

@@

% ENGLISH ABSTRACT / SUMMARY
\CustChapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}
%\chapter*{Abstract}
%\thispagestyle{empty}%
\todo{Write abstract ...}

@@

% PREFACE AND ACKNOWLEDGEMENTS
\CustChapter*{Preface}%
\addcontentsline{toc}{chapter}{Preface}
%\thispagestyle{empty}%
The present thesis is submitted in partial fulfillment of the requirements for the degree of \textit{Philosophiae Doctor} (Ph.D.) at the Faculty of Medicine at the Norwegian University of Science and Technology (NTNU). The research was funded by \textit{Medical Imaging Laboratory} (MI-Lab), and was carried out at the Department of Circulation and Medical Imaging. The main supervisor has been Professor Sverre Holm  in the Department of Informatics, University of Oslo, and Professor II at MI-Lab, NTNU. Co-supervisors have been PhD Stein Inge Rabben, PhD Erik Steen and Professor Hans Torp.

@@

\CustChapter*{List of publications}
\addcontentsline{toc}{chapter}{List of publications}

This thesis is based on the following five papers, referred to in the text by their Roman numerals (I-V): 
\begin{enumerate}[I]
\renewcommand\labelenumi{\bfseries\theenumi}
	\item J. I. Buskenes, \textbf{J. P. \AA{}sen}, C.-I. C. Nilsen and A. Austeng, "An optimised GPU implementation of the MVDR beamformer for active sonar imaging", {\it  IEEE Transactions on Oceanic Engineering, submitted}.
	\item \textbf{J. P. \AA{}sen}, J. I. Buskenes, C.-I. C. Nilsen, A. Austeng and S. Holm, "Implementing Capon beamforming on a GPU for real-time cardiac ultrasound imaging", {\it IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control, vol. 61, no. 1, pp. \todo{add pages} Jan 2014}.
 	\item \textbf{J. P. \AA{}sen}, A. Austeng and S. Holm, "Capon beamforming and moving objects - An analysis of lateral shift-invariance", {\it IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control, submitted}.
	\item \textbf{J. P. \AA{}sen}, E. Steen, G. Kiss, A. Thorstensen and S. I. Rabben, "Adaptive volume rendering of cardiac 3D ultrasound images - utilizing blood pool statistics", {\it Proc. SPIE Medical Imaging 2012 \todo{add pages}}.
	\item \textbf{J. P. \AA{}sen} and S. Holm, "Huygens on speed: Interactive simulation of ultrasound pressure fields", {\it Proc. IEEE Ultrasonics Symposium 2012 \todo{add pages}}.
\end{enumerate}

\CustChapter*{Related publications}
\addcontentsline{toc}{chapter}{Related publications}
The following papers are related to the included papers, and are referred to in the text by their Roman numerals:

@@

	\item \textbf{J. P. \AA{}sen}, J. I. Buskenes, C.-I. C. Nilsen, A. Austeng and S. Holm, "Implementing Capon Beamforming on the GPU for Real-Time Cardiac Ultrasound Imaging", {\it Proc. IEEE Ultrasonics Symposium 2012} \todo{add pages}.

	\item J. I. Buskenes, \textbf{J. P. \AA{}sen}, C.-I. C. Nilsen and A. Austeng, "Adapting the Minimum variance beamformer to a graphics processing unit for active sonar imaging systems", {\it Proc. Meetings on Acoustics 2013} \todo{add pages?}.

	\item G. Kiss, E. Steen, \textbf{J. P \AA{}sen} and H. Torp, "GPU volume rendering in 3D echocardiography: real-time pre-processing and ray-casting", {\it Proc. IEEE Ultrasonics Symposium 2010} \todo{add pages}.

@@

	\item E. S. Br\o{}nstad, \textbf{J. P. \AA{}sen}, H. Torp and G. Kiss, "Visibility driven visualization of 3D cardiac ultrasound data on the GPU", {\it Proc. IEEE Ultrasonics Symposium 2012} \todo{add pages}.
\end{enumerate}

\newpage\thispagestyle{empty}
\pagestyle{fancy}

%

\cleardoublepage
\addcontentsline{toc}{chapter}{Contents}
\renewcommand*\contentsname{Contents}
\tableofcontents

\clearpage
\setcounter{page}{1}
\renewcommand{\thepage}{\arabic{page}}

\renewcommand*\thesection{\arabic{section}}

%%%% CHAPTER 1 %%%%
\begin{bibunit}[ieeetr]
\CustChapter*{Introduction} 
\addcontentsline{toc}{chapter}{Introduction}
\runningtitle{Introduction}
\input{./Introduction/introduction}
\newpage\addcontentsline{toc}{section}{References}
\putbib[bibIntroduction]
\end{bibunit}

\setcounter{section}{0}
\setcounter{chapter}{1}

%%%% CHAPTER 2 %%%%
\begin{bibunit}[ieeetr]
\CustChapter*{Background}
\addcontentsline{toc}{chapter}{Background} 
\runningtitle{Background}
\input{./Background/background}
\newpage\addcontentsline{toc}{section}{References}
\putbib[bibBackground]
\end{bibunit}

\setcounter{chapter}{0}

%%%% Paper 1 %%%%
\begin{bibunit}[ieeetr]
\CustChapterPaper{An Optimised GPU Implementation of the MVDR Beamformer for Active Sonar Imaging}
\runningtitle{GPU MVDR Beamformer for Active Sonar Imaging}
\authors{
	Jo Inge Buskenes$^{1}$, 
    	\textbf{Jon Petter \AA{}sen}$^{2}$, 
    	Carl-Inge C. Nilsen$^{1}$ and
    	Andreas Austeng$^{1}$
} 
{
	$^{1}$Department of Informatics, University of Oslo, Oslo, Norway\\
    	$^{2}$Medical Imaging Lab (MI-Lab), Norwegian University of Science and Technology, Trondheim, Norway
}
\noindent \textit{IEEE Transactions on Oceanic Engineering, submitted}
%\newpage\input{./CaponSonarGPU/CaponSonarGPU}
%\newpage\addcontentsline{toc}{section}{References}
\putbib[bibCaponSonarGPU]
\end{bibunit}

%%%% Paper 2 %%%%
\begin{bibunit}[ieeetr]
\CustChapterPaper{Implementing Capon Beamforming on a GPU for Real-Time Cardiac Ultrasound Imaging}
\runningtitle{GPU Capon Beamformer for Cardiac Ultrasound Imaging}
\authors{
	\textbf{Jon Petter \AA{}sen}$^{1}$,
    	Jo Inge Buskenes$^{2}$,  
    	Carl-Inge C. Nilsen$^{2}$,
    	Andreas Austeng$^{2}$ and
    	Sverre Holm$^{1,2}$
} 
{
	$^{1}$Medical Imaging Lab (MI-Lab), Norwegian University of Science and Technology, Trondheim, Norway\\
    	$^{2}$Department of Informatics, University of Oslo, Oslo, Norway
}
\noindent \textit{IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control, vol. 61, Jan 2014}
%\input{./CaponCardiacGPU/CaponCardiacGPU}
%\newpage\addcontentsline{toc}{section}{References}
\putbib[bibCaponCardiacGPU]
\end{bibunit}

%%%% Paper 3 %%%%
\begin{bibunit}[ieeetr]
\CustChapterPaper{Capon Beamforming and Moving Objects - An Analysis of Lateral Shift-Invariance}
\runningtitle{Capon Beamforming and Moving Objects}
\authors{
	\textbf{Jon Petter \AA{}sen}$^{1}$, 
    	Andreas Austeng$^{2}$ and
    	Sverre Holm$^{1,2}$
} 
{
	$^{1}$Medical Imaging Lab (MI-Lab), Norwegian University of Science and Technology, Trondheim, Norway\\
    	$^{2}$Department of Informatics, University of Oslo, Oslo, Norway
}
\noindent \textit{IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control, submitted}
%\input{./CaponMovingObjects/CaponMovingObjects}
%\newpage\addcontentsline{toc}{section}{References}
\putbib[bibCaponMovingObjects]
\end{bibunit}

%%%% Paper 4 %%%%
\begin{bibunit}[ieeetr]
\CustChapterPaper{Adaptive Volume Rendering of Cardiac 3D Ultrasound Images - Utilizing Blood Pool Statistics}
\runningtitle{Adaptive Volume Rendering of Cardiac Ultrasound}
\authors{
	\textbf{Jon Petter \AA{}sen}$^{1}$,
	Erik Steen$^2$,
	Gabriel Kiss$^{3,4}$,
	Anders Thorstensen$^{1,5}$,
	Stein Inge Rabben$^2$
}
{
$^{1}$Medical Imaging Lab (MI-Lab), Norwegian University of Science and Technology, Trondheim, Norway\\
$^{2}$ GE Vingmed Ultrasound, Horten, Norway\\
$^{3}$ Norwegian University of Science and Technology, ISB - Department of Circulation and Medical Imaging, Trondheim, Norway\\
$^{4}$ St. Olavs Hospital, Trondheim, Norway\\
$^{5}$ Department of Cardiology, St. Olavs Hospital, Trondheim, Norway
}
\noindent \textit{Proc. SPIE Medical Imaging 2012 \todo{add pages}}
%\input{./AdaptiveVolumeRendering/AdaptiveVolumeRendering}
%\newpage\addcontentsline{toc}{section}{References}
\putbib[bibAdaptiveVolumeRendering]
\end{bibunit}

%%%% Paper 5 %%%%
\begin{bibunit}[ieeetr]
\CustChapterPaper{Huygens on Speed: Interactive Simulation of Ultrasound Pressure Fields}
\runningtitle{Huygens on speed}
\authors{\textbf{Jon Petter \AA{}sen}$^1$ and Sverre Holm$^{1,2}$}
{
	$^{1}$Medical Imaging Lab (MI-Lab), Norwegian University of Science and Technology, Trondheim, Norway\\
    	$^{2}$Department of Informatics, University of Oslo, Oslo, Norway
}
\noindent \textit{Proc. IEEE Ultrasonics Symposium 2012 \todo{add pages}}
%\input{./Hos/Hos}
%\newpage\addcontentsline{toc}{section}{References}
\putbib[bibHos]
\end{bibunit}
